---
title: "Final Document"
author: "Karthik Venkatesh"
date: "December 5 2018"
output:
  
  html_document:
    theme: cosmo
    toc: yes
    code_folding: hide
  word_document: default
  pdf_document:
    
    toc: yes
  github_document:
    toc: yes
---
* * *

#Data Cleaning
## Data Files Generated: 

**Data of the species BeachPlum at the different sites its present.**

####For Different Sites where BeachPlum is Present

 Site_D_BeachPlum.csv
 
 Site_E_BeachPlum.csv
 
 Site_G_BeachPlum.csv
 

**Data of the Species BeachPlum Intensity for different years 2016,2017,2018**

####For Year 2016
 SiteD_BeachPlum_2016.csv
 
 SiteE_BeachPlum_2016.csv
 
 SiteG_BeachPlum_2016.csv
 
####For Year 2017
 
 SiteD_BeachPlum_2017.csv
 
 SiteE_BeachPlum_2017.csv
 
 SiteG_BeachPlum_2017.csv

####For Year 2018
 
 SiteD_BeachPlum_2018.csv
 
 SiteE_BeachPlum_2018.csv
 
 SiteG_BeachPlum_2018.csv


**Temperature Data file from the different sites recorded by the temperature logger for different years.**

####For Site D
 
 Min.Max_SiteDJune2016.csv
 
 Min.Max_SiteDJune2017.csv
 
 Min.Max_SiteDMay2018.csv
 
####For Site E
 Min.Max_SiteEJune2016.csv
 
 Min.Max_SiteEJune2017.csv
 
 Min.Max_SiteEMay2018.csv
 
####For Site G
 Min.Max_SiteGJune2016.csv
 
 Min.Max_SiteGJune2017.csv
 
 Min.Max_SiteGMay2018.csv

## Steps Taken to Clean the Data:

Download the data from National Phenology network site by giving the necessary inputs like data range, species and state. 
Next Select phenophase such as flowers, fruits, leaves etc.
Select the partner groups as Linda Loring Foundation, Source data set as Natures notebook then select the optional fields required like Site Name and Phenophase category.

From the Statusintensity file downloaded we transform the excel file with selected columns and filters.
For our case study we are interested in taking the BeachPlum plant to observe its Breaking of bud over the diffrent sites at Linda Loring foundation over the years 2016,2017,2018.

We transform and breakdown the phenophase data intensity of the species BeachPlum based on 
1)Phenophase-Breakingbud
2)Site where the Plant beachplum was Phenophase Intensity was observed
3)Year the phenophase was observed

We further change the intensity values in the excel files we obtained to a cardinal scale ,so that we can visualize the data.

Give the intensity values in the BeachPlum Intensity files a cardinal scale.

 0---- -9999  
 1----Less than 3  
 2----3 to 10  
 3----11 to 100  
 4----101 to 1000  
 5----1001 to 10000  
 6----more than 10000  






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r initiation, echo=TRUE, message=FALSE, warning=FALSE} 
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_knit$set(root.dir = "D:/MS/D2D Final/Data Source/BeachPlum/Data By Site-Year") 
```

Invoke the required libraries required for the visualizations and statistics.
    
```{r getlibrary, warning=FALSE,message=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
```
##Cleaning Phenophase Intensity Data

### Loading the data 
 
Load the AllSpecies.csv file into a dataframe variable using the following R script
    
```{r getDataAllSpecies, echo=TRUE}
AllSpecies <- read.csv("AllSpecies.csv")
View(AllSpecies)    
```
### Filtering Columns
Use the select function to select only the required important columns for the BeachPlum data ,we filter the data based on the phenophase "Breaking leaf buds"
  
```{r filterbreakingbud,echo=TRUE}
BreakingBud=subset(AllSpecies,AllSpecies$Phenophase_Name=="Breaking leaf buds",select =c("Site_Name","Common_Name","Phenophase_Name","Observation_Date","Day_of_Year","Phenophase_Status","Intensity_Category_ID","Intensity_Value"))
View(BreakingBud)
write.csv(BreakingBud,file = "BreakingBud.csv")
```

Before we go further filter the data its really important to change the date format in excel to short date. Goto the excel file breakinbud.csv,select the Observation_Date column and then change it to type short date instead of general.
There seems to some kind of issue with the excel file generated from the R markdown, we need to ensure that the Observation Date is of Date Type format before we can filter the BeachPlum data based on Year.

Now we filter the data set based on the Sites having beach plum plant that is Sites D,E,G

###Filter Based on the Sites
Now we filter Intensity data obtained from National Phenology Network based on the sites present at the Linda loring foundation.

```{r getDataBreakingBud,echo=TRUE,message=FALSE}
BreakingBudData <- read.csv("BreakingBud.csv")
BreakingBudData$Observation_Date<-as.Date(BreakingBudData$Observation_Date,format("%m/%d/%Y"))
View(BreakingBudData)    
str(BreakingBudData)
```
##### Beach Plum-Site D

Site D

```{r filteringSites Site D and Species is BeachPlum,echo=TRUE,warning=FALSE,message=FALSE}
Site_D_BeachPlumBud <- subset(BreakingBudData,Site_Name=="Site D" & Common_Name=="beach plum")
View(Site_D_BeachPlumBud)
write.csv(Site_D_BeachPlumBud,file="Site_D_BeachPlum.csv")

```
##### Beach Plum-Site E
Site E

```{r filteringSites Site E and Species is BeachPlum,echo=TRUE,warning=FALSE,message=FALSE}
Site_E_BeachPlumBud <- subset(BreakingBudData,Site_Name=="Site E" & Common_Name=="beach plum")
View(Site_E_BeachPlumBud)
write.csv(Site_E_BeachPlumBud,file="Site_E_BeachPlum.csv")
```


##### Beach Plum-Site G
Site G

```{r filteringSites Site G and Species is BeachPlum,echo=TRUE}
Site_G_BeachPlumBud <- subset(BreakingBudData,Site_Name=="Site G" & Common_Name=="beach plum")
View(Site_G_BeachPlumBud)
write.csv(Site_G_BeachPlumBud,file="Site_G_BeachPlum.csv")
```


##Filtering Intensity data observed over the Years 
Next we further prepare the data for plotting of the breaking bud intensity observed at the different sites over the years.
We use the functions as.Date to change the Observation Date from character to Date format in order to filter the data based on the years.

###BeachPlum BreakingBud Intensity Observed at Site D 
```{r getBeachPlumDataSiteD, echo=TRUE}
SiteD_BeachPlum<-read.csv("Site_D_BeachPlum.csv",stringsAsFactors = FALSE)
SiteD_BeachPlum$Observation_Date<-as.Date(SiteD_BeachPlum$Observation_Date,format("%m/%d/%Y"))
View(SiteD_BeachPlum)
str(SiteD_BeachPlum)
```
####For the Year 2016
```{r filteryear2016SiteD, echo=TRUE }
SiteD_BeachPlum_2016<-subset(SiteD_BeachPlum,format(as.Date(SiteD_BeachPlum$Observation_Date),"%Y")==2016)
View(SiteD_BeachPlum)
write.csv(SiteD_BeachPlum_2016,file = "SiteD_BeachPlum_2016.csv")
```
####For the Year 2017
```{r filteryear2017SiteD, echo=TRUE }
SiteD_BeachPlum_2017<-subset(SiteD_BeachPlum, format(as.Date(SiteD_BeachPlum$Observation_Date),"%Y")==2017)
write.csv(SiteD_BeachPlum_2017,file = "SiteD_BeachPlum_2017.csv")
```
####For the Year 2018
```{r filteryear2018SiteD, echo=TRUE }
SiteD_BeachPlum_2018<-subset(SiteD_BeachPlum, format(as.Date(SiteD_BeachPlum$Observation_Date),"%Y")==2018)
write.csv(SiteD_BeachPlum_2018,file = "SiteD_BeachPlum_2018.csv")
```
###BeachPlum Breaking Bud Observed at Site E

```{r getBeachPlumDataSiteE, echo=TRUE}

SiteE_BeachPlum<-read.csv("Site_E_BeachPlum.csv",stringsAsFactors = FALSE)
SiteE_BeachPlum$Observation_Date<-as.Date(SiteE_BeachPlum$Observation_Date,format("%m/%d/%Y"))
View(SiteE_BeachPlum)
str(SiteE_BeachPlum)
```
####For the Year 2016
```{r filteryear2016SiteE, echo=TRUE }
SiteE_BeachPlum_2016<-subset(SiteE_BeachPlum, format(as.Date(SiteE_BeachPlum$Observation_Date),"%Y")==2016)
write.csv(SiteE_BeachPlum_2016,file = "SiteE_BeachPlum_2016.csv")
```
####For the Year 2017
```{r filteryear2017SiteE, echo=TRUE }
SiteE_BeachPlum_2017<-subset(SiteE_BeachPlum, format(as.Date(SiteE_BeachPlum$Observation_Date),"%Y")==2017)
write.csv(SiteE_BeachPlum_2017,file = "SiteE_BeachPlum_2017.csv")
```
####For the Year 2018
```{r filteryear2018SiteE, echo=TRUE }
SiteE_BeachPlum_2018<-subset(SiteE_BeachPlum, format(as.Date(SiteE_BeachPlum$Observation_Date),"%Y")==2018)
write.csv(SiteE_BeachPlum_2018,file = "SiteE_BeachPlum_2018.csv")
```
###BeachPlum Breaking Bud Observed at Site G

```{r getBeachPlumDataSiteG, echo=TRUE}

SiteG_BeachPlum<-read.csv("Site_G_BeachPlum.csv",stringsAsFactors = FALSE)
SiteG_BeachPlum$Observation_Date<-as.Date(SiteG_BeachPlum$Observation_Date,format("%m/%d/%Y"))
View(SiteG_BeachPlum)
str(SiteG_BeachPlum)
```
####For the Year 2016
```{r filteryear2016SiteG, echo=TRUE }
SiteG_BeachPlum_2016<-subset(SiteG_BeachPlum, format(as.Date(SiteG_BeachPlum$Observation_Date),"%Y")==2016)
write.csv(SiteG_BeachPlum_2016,file = "SiteG_BeachPlum_2016.csv")
```
####For the Year 2017
```{r filteryear2017SiteG, echo=TRUE }
SiteG_BeachPlum_2017<-subset(SiteG_BeachPlum, format(as.Date(SiteG_BeachPlum$Observation_Date),"%Y")==2017)
write.csv(SiteG_BeachPlum_2017,file = "SiteG_BeachPlum_2017.csv")
```
####For the Year 2018
```{r filteryear2018SiteG, echo=TRUE }
SiteG_BeachPlum_2018<-subset(SiteG_BeachPlum, format(as.Date(SiteG_BeachPlum$Observation_Date),"%Y")==2018)
write.csv(SiteG_BeachPlum_2018,file = "SiteG_BeachPlum_2018.csv")
```





##Cleaning the Temperature Data Set
In order to measure the impact of temperature on the breakingbud intensity we need to clean the temperature data,convert the dates to day so that we could have a common x axis in the plots for both the intensity data set and temperature data.


####Convert the dates to days in the data set

```{r adding days to temperature data Site D,echo=TRUE,warning=FALSE}
June2017_siteD <- read.csv("Site_D.csv", header=TRUE)
June2017_siteD$Date <- format(as.POSIXct(strptime(June2017_siteD$ï..Date.Time,"%m/%d/%Y %H:%M",tz="")) ,format = "%m/%d/%Y")
June2017_siteD$Day <- format(as.POSIXct(strptime(June2017_siteD$ï..Date.Time,"%m/%d/%Y",tz="")) ,format = "%j")
write.csv(June2017_siteD, "SiteD_June2017.csv")
```

```{r adding days to temperature data Site E,echo=TRUE,warning=FALSE}
June2017_siteE <- read.csv("Site_E.csv", header=TRUE)
June2017_siteE$Date <- format(as.POSIXct(strptime(June2017_siteE$ï..Date.Time,"%m/%d/%Y %H:%M",tz="")) ,format = "%m/%d/%Y")
June2017_siteE$Day <- format(as.POSIXct(strptime(June2017_siteE$ï..Date.Time,"%m/%d/%Y",tz="")) ,format = "%j")
write.csv(June2017_siteE, "SiteE_June2017.csv")
```

```{r adding days to temperature data Site G,echo=TRUE}
June2017_siteG <- read.csv("Site_G.csv", header=TRUE)
June2017_siteG$Date <- format(as.POSIXct(strptime(June2017_siteG$ï..Date.Time,"%m/%d/%Y %H:%M",tz="")) ,format = "%m/%d/%Y")
June2017_siteG$Day <- format(as.POSIXct(strptime(June2017_siteG$ï..Date.Time,"%m/%d/%Y",tz="")) ,format = "%j")
write.csv(June2017_siteG, "SiteG_June2017.csv")
```


####Finding the average and minimum temperature.
We need to find the minimum temperature for the different sites for the different years 2016,2017,2018. So that we can compare the temperature of the day in a year with the Breaking bud intensity of Beachplum for that day.


#####Site D Min,avg Temperature
```{r getting the minimum temperature Site D,echo=TRUE}
siteD_June2017 <- read.csv("SiteD_June2017.csv")

avg_siteD_2017 <- aggregate(Temp ~ Date, siteD_June2017, mean)

min_siteD_2017 <- aggregate(Temp ~ Date, siteD_June2017, min)

June2017_SiteD <- merge(min_siteD_2017, avg_siteD_2017, by="Date")

names(June2017_SiteD)[2]<-"Min Temp"

names(June2017_SiteD)[3]<-"Avg Temp"

June2017_SiteD$Day <- format(as.POSIXct(strptime(June2017_SiteD$Date,"%m/%d/%Y",tz="")) ,format = "%j")

write.csv(June2017_SiteD, "Min.Max_SiteDJune2017.csv")

```
#####Site E Min,avg Temperature
```{r getting the minimum temperature Site E,echo=TRUE}
siteE_June2017 <- read.csv("SiteE_June2017.csv")

avg_siteE_2017 <- aggregate(Temp ~ Date, siteE_June2017, mean)

min_siteE_2017 <- aggregate(Temp ~ Date, siteE_June2017, min)

June2017_SiteE <- merge(min_siteE_2017, avg_siteE_2017, by="Date")

names(June2017_SiteE)[2]<-"Min Temp"

names(June2017_SiteE)[3]<-"Avg Temp"

June2017_SiteE$Day <- format(as.POSIXct(strptime(June2017_SiteE$Date,"%m/%d/%Y",tz="")) ,format = "%j")

write.csv(June2017_SiteE, "Min.Max_SiteEJune2017.csv")

```

#####Site G Min,avg Temperature
```{r getting the minimum temperature Site G,echo=TRUE}
siteG_June2017 <- read.csv("SiteG_June2017.csv")

avg_siteG_2017 <- aggregate(Temp ~ Date, siteG_June2017, mean)

min_siteG_2017 <- aggregate(Temp ~ Date, siteG_June2017, min)

June2017_SiteG <- merge(min_siteG_2017, avg_siteG_2017, by="Date")

names(June2017_SiteG)[2]<-"Min Temp"

names(June2017_SiteG)[3]<-"Avg Temp"

June2017_SiteG$Day <- format(as.POSIXct(strptime(June2017_SiteG$Date,"%m/%d/%Y",tz="")) ,format = "%j")

write.csv(June2017_SiteG, "Min.Max_SiteGJune2017.csv")

```

#DescriptiveStatistics

Now lets perform some descriptive statistics on the data we have. A histogram helps us to get an idea on the frequency distribution of the values. 




##Intensity Values

Lets plot the Histogram for the Breaking Bud Intensity value.

###SiteD

```{r frequencyofintenstiy Site D ,echo=TRUE}
SiteD<-read.csv("Site_D_BeachPlum.csv")

hist(SiteD$Intensity_Value, col="blue", xlab="Site D BeachPlum BreakingBudIntensity", main="Breaking Bud Intensity-Site D")

```



###SiteE


```{r frequencyofintenstiy Site E ,echo=TRUE}
SiteE<-read.csv("Site_E_BeachPlum.csv")

hist(SiteE$Intensity_Value, col="blue", xlab="Site E BeachPlum  BreakingBudIntensity", main="Breaking Bud Intensity-Site E")
```

###SiteG

```{r frequencyofintenstiy Site G ,echo=TRUE}
SiteG<-read.csv("Site_G_BeachPlum.csv")

hist(SiteG$Intensity_Value, col="blue", xlab="Site G BeachPlum BreakingBudIntensity", main="Breaking Bud Intensity-Site G")
```

##Temperature Values

Lets Plot an Histogram to see the distribution of the Minimum temperature across the Years and at different sites.

###Year 2016

####Site D

```{r frequencyoftemperature Site D 2016,echo=TRUE,warning=FALSE}
SiteDTemp2016<-read.csv("Min.Max_SiteDJune2016.csv")

ggplot(data=SiteDTemp2016, aes(SiteDTemp2016$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site D Year 2016") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```


####Site E

```{r frequencyoftemperature Site E 2016,echo=TRUE,warning=FALSE}
SiteETemp2016<-read.csv("Min.Max_SiteEJune2016.csv")

ggplot(data=SiteETemp2016, aes(SiteETemp2016$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site E Year 2016") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```

####Site G


```{r frequencyoftemperature Site G 2016,echo=TRUE,warning=FALSE}
SiteGTemp2016<-read.csv("Min.Max_SiteGJune2016.csv")

ggplot(data=SiteGTemp2016, aes(SiteGTemp2016$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site G Year 2016") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```




###Year 2017


####Site D

```{r frequencyoftemperature Site D 2017,echo=TRUE,warning=FALSE}
SiteDTemp2017<-read.csv("Min.Max_SiteDJune2017.csv")

ggplot(data=SiteDTemp2017, aes(SiteDTemp2017$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site D Year 2017 ") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```


####Site E

```{r frequencyoftemperature Site E 2017,echo=TRUE,warning=FALSE}
SiteETemp2017<-read.csv("Min.Max_SiteEJune2017.csv")

ggplot(data=SiteETemp2017, aes(SiteETemp2017$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site E Year 2017 ") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```


####Site G

```{r frequencyoftemperature Site G 2017,echo=TRUE,warning=FALSE}
SiteGTemp2017<-read.csv("Min.Max_SiteGJune2017.csv")

ggplot(data=SiteGTemp2017, aes(SiteGTemp2017$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site G Year 2017 ") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```




###Year 2018

####Site D

```{r frequencyoftemperature Site D 2018,echo=TRUE,warning=FALSE}
SiteDTemp2018<-read.csv("Min.Max_SiteDMay2018.csv")

ggplot(data=SiteDTemp2018, aes(SiteDTemp2018$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site D Year 2018 ") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```


####Site E
```{r frequencyoftemperature Site E 2018,echo=TRUE,warning=FALSE}
SiteETemp2018<-read.csv("Min.Max_SiteEMay2018.csv")

ggplot(data=SiteETemp2018, aes(SiteETemp2018$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site E Year 2018 ") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```

####Site G

```{r frequencyoftemperature Site G 2018,echo=TRUE,warning=FALSE}
SiteGTemp2018<-read.csv("Min.Max_SiteGMay2018.csv")

ggplot(data=SiteGTemp2018, aes(SiteGTemp2018$Min.Temp)) + 
  geom_histogram( binwidth = 0.5,
                 col="red", 
                 fill="green", 
                 alpha = .2) + 
  labs(title="Histogram for Min Temperature Site G Year 2018 ") +
  labs(x="Min Temperature", y="Frequency") + 
  xlim(c(0,20)) +
  ylim(c(0,18))
```





#Visualization



##Phenophase Intensity Vs Minimum Temperature of BeachPlum -2016

###Site D 

```{r read BeachPlum2016 intensitydata SiteD,echo=TRUE,warning=FALSE}

SiteD_Beach_2016<-read.csv("SiteD_BeachPlum_2016.csv")



fig1<-ggplot(SiteD_Beach_2016, aes(SiteD_Beach_2016$Day_of_Year, SiteD_Beach_2016$Intensity_Value
)) +ggtitle("Beach Plum Breaking Leaf bud Intensity value throughout Year 2016 at Site D")+ geom_line() +geom_point() +xlab("Year 2016") + ylab("Breaking Bud IntensityValue")+xlim(c(100,200))


SiteDTemp2016<-read.csv("Min.Max_SiteDJune2016.csv")

SiteDTemp2016$Date<-as.Date(SiteDTemp2016$Date,format("%m/%d/%Y"))


fig2<-ggplot(SiteDTemp2016, aes(SiteDTemp2016$Day, SiteDTemp2016$Min.Temp
))+ggtitle("Temperature Plot at Site D in 2016") + geom_line(color="Red") + xlab("Year 2016") + ylab("MinTemp")


grid.arrange(fig1,fig2,nrow=2)

```


###Site E


```{r read BeachPlum2016 intensitydata Site E,echo=TRUE,warning=FALSE}

SiteE_Beach_2016<-read.csv("SiteE_BeachPlum_2016.csv")



fig7<-ggplot(SiteE_Beach_2016, aes(SiteE_Beach_2016$Day_of_Year, SiteE_Beach_2016$Intensity_Value
)) +ggtitle("Beach Plum Breaking Bud Intensity value throughout year 2016 at Site E")+ geom_line() +geom_point()+ xlab("Year 2016") + ylab("Breaking Bud Intensity Value")+xlim(c(100,200))


SiteETemp2016<-read.csv("Min.Max_SiteEJune2016.csv")

SiteETemp2016$Date<-as.Date(SiteETemp2016$Date,format("%m/%d/%Y"))


fig8<-ggplot(SiteETemp2016, aes(SiteETemp2016$Day, SiteETemp2016$Min.Temp
))+ggtitle("Temperature Plot at Site E in 2016") + geom_line(color="Red") + xlab("Year 2016") + ylab("MinTemp")


grid.arrange(fig7,fig8,nrow=2)

```


###Site G


```{r read BeachPlum2016 intensitydata Site G,echo=TRUE,warning=FALSE}

SiteG_Beach_2016<-read.csv("SiteG_BeachPlum_2016.csv")



fig9<-ggplot(SiteG_Beach_2016, aes(SiteG_Beach_2016$Day_of_Year, SiteG_Beach_2016$Intensity_Value
)) +ggtitle("Beach Plum Breaking Bud Intensity value throughout year 2016 at Site G")+ geom_line() +geom_point()+ xlab("Year 2016") + ylab("Breaking Bud Intensity Value")+xlim(c(100,200))


SiteGTemp2016<-read.csv("Min.Max_SiteGJune2016.csv")

SiteGTemp2016$Date<-as.Date(SiteGTemp2016$Date,format("%m/%d/%Y"))


fig10<-ggplot(SiteGTemp2016, aes(SiteGTemp2016$Day, SiteGTemp2016$Min.Temp
))+ggtitle("Temperature Plot at Site G in 2016") + geom_line(color="Red") + xlab("Year 2016") + ylab("MinTemp")


grid.arrange(fig9,fig10,nrow=2)

```







##Phenophase Intensity Vs Minimum Temperature of BeachPlum -2017

###Site D

```{r read BeachPlum2017 intensitydata SiteD,echo=TRUE,warning=FALSE}

SiteD_Beach_2017<-read.csv("SiteD_BeachPlum_2017.csv")



fig3<-ggplot(SiteD_Beach_2017, aes(SiteD_Beach_2017$Day_of_Year, SiteD_Beach_2017$Intensity_Value
)) +ggtitle("Beach Plum Intensity value throughout year 2017 at Site D")+ geom_line() + geom_point()+xlab("Year 2017") + ylab("Breaking Bud Intensity Value")+xlim(c(100,200))



SiteDTemp2017<-read.csv("Min.Max_SiteDJune2017.csv")

SiteDTemp2017$Date<-as.Date(SiteDTemp2017$Date,format("%m/%d/%Y"))


fig4<-ggplot(SiteDTemp2017, aes(SiteDTemp2017$Day, SiteDTemp2017$Min.Temp
))+ggtitle("Temperature Plot Site D") + geom_line(color="Red") + xlab("Year 2017") + ylab("MinTemp")


grid.arrange(fig3,fig4,nrow=2)
```

###Site E


```{r read BeachPlum2017 intensitydata SiteE,echo=TRUE,warning=FALSE}

SiteE_Beach_2017<-read.csv("SiteE_BeachPlum_2017.csv")



fig11<-ggplot(SiteE_Beach_2017, aes(SiteE_Beach_2017$Day_of_Year, SiteE_Beach_2017$Intensity_Value
)) +ggtitle("Beach Plum Intensity value throughout year 2017 at Site E")+ geom_point() +geom_line()+ xlab("Year 2017") + ylab("Breaking Bud Intensity Value")+xlim(c(100,200))



SiteETemp2017<-read.csv("Min.Max_SiteEJune2017.csv")

SiteETemp2017$Date<-as.Date(SiteETemp2017$Date,format("%m/%d/%Y"))


fig12<-ggplot(SiteETemp2017, aes(SiteETemp2017$Day, SiteETemp2017$Min.Temp
))+ggtitle("Temperature Plot Site E") + geom_line(color="Red") + xlab("Year 2017") + ylab("MinTemp")


grid.arrange(fig11,fig12,nrow=2)
```


###SiteG


```{r read BeachPlum2017 intensitydata SiteG,echo=TRUE,warning=FALSE}

SiteG_Beach_2017<-read.csv("SiteG_BeachPlum_2017.csv")



fig13<-ggplot(SiteG_Beach_2017, aes(SiteG_Beach_2017$Day_of_Year, SiteG_Beach_2017$Intensity_Value
)) +ggtitle("Beach Plum Intensity value throughout year 2017 at Site G")+ geom_point() +geom_line()+ xlab("Year 2017") + ylab("Breaking Bud Intensity Value")+xlim(c(100,200))



SiteGTemp2017<-read.csv("Min.Max_SiteGJune2017.csv")

SiteGTemp2017$Date<-as.Date(SiteGTemp2017$Date,format("%m/%d/%Y"))


fig14<-ggplot(SiteGTemp2017, aes(SiteGTemp2017$Day, SiteGTemp2017$Min.Temp
))+ggtitle("Temperature Plot Site G") + geom_line(color="Red") + xlab("Year 2017") + ylab("MinTemp")


grid.arrange(fig13,fig14,nrow=2)
```



##Phenophase Intensity Vs Minimum Temperature of BeachPlum-2018

###Site D

```{r read BeachPlum2018 intensitydata SiteD,echo=TRUE,warning=FALSE}

SiteD_Beach_2018<-read.csv("SiteD_BeachPlum_2018.csv")



fig5<-ggplot(SiteD_Beach_2018, aes(SiteD_Beach_2018$Day_of_Year, SiteD_Beach_2018$Intensity_Value
)) +ggtitle("Beach Plum Intensity value throughout year 2018 at Site D")+ geom_line() +geom_point()+ xlab("Year 2018") + ylab("BreakingBud Intensity Value")+xlim(c(100,200))



SiteDTemp2018<-read.csv("Min.Max_SiteDMay2018.csv")

SiteDTemp2018$Date<-as.Date(SiteDTemp2018$Date,format("%m/%d/%Y"))


fig6<-ggplot(SiteDTemp2018, aes(SiteDTemp2018$Day, SiteDTemp2018$Min.Temp
))+ggtitle("Temperature Plot Site D ") + geom_line(color="Red") + xlab("Year 2018") + ylab("MinTemp")+xlim(c(100,200))


grid.arrange(fig5,fig6,nrow=2)
```


###Site E


```{r read BeachPlum2018 intensitydata SiteE,echo=TRUE,warning=FALSE}

SiteE_Beach_2018<-read.csv("SiteE_BeachPlum_2018.csv")



fig15<-ggplot(SiteE_Beach_2018, aes(SiteE_Beach_2018$Day_of_Year, SiteE_Beach_2018$Intensity_Value
)) +ggtitle("Beach Plum Intensity value throughout year 2018 at Site E")+ geom_line() +geom_point()+ xlab("Year 2018") + ylab("BreakingBud Intensity Value")+xlim(c(100,200))



SiteETemp2018<-read.csv("Min.Max_SiteEMay2018.csv")

SiteETemp2018$Date<-as.Date(SiteETemp2018$Date,format("%m/%d/%Y"))


fig16<-ggplot(SiteETemp2018, aes(SiteETemp2018$Day, SiteETemp2018$Min.Temp
))+ggtitle("Temperature Plot Site D ") + geom_line(color="Red") + xlab("Year 2018") + ylab("MinTemp")+xlim(c(100,200))


grid.arrange(fig15,fig16,nrow=2)
```


###Site G


```{r read BeachPlum2018 intensitydata SiteG,echo=TRUE,warning=FALSE}

SiteG_Beach_2018<-read.csv("SiteG_BeachPlum_2018.csv")



fig15<-ggplot(SiteG_Beach_2018, aes(SiteG_Beach_2018$Day_of_Year, SiteG_Beach_2018$Intensity_Value
)) +ggtitle("Beach Plum Intensity value throughout year 2018 at Site G")+ geom_line() +geom_point()+ xlab("Year 2018") + ylab("BreakingBud Intensity Value")+xlim(c(100,200))



SiteETemp2018<-read.csv("Min.Max_SiteEMay2018.csv")

SiteETemp2018$Date<-as.Date(SiteETemp2018$Date,format("%m/%d/%Y"))


fig16<-ggplot(SiteETemp2018, aes(SiteETemp2018$Day, SiteETemp2018$Min.Temp
))+ggtitle("Temperature Plot Site D ") + geom_line(color="Red") + xlab("Year 2018") + ylab("MinTemp")+xlim(c(100,200))


grid.arrange(fig15,fig16,nrow=2)
```




